Posterior summarisation in Bayesian phylogenetics using Tracer 1.6

### 2017-08-05 manuscript/tracer16.tex
better title
merge and remove figures; we have too many

% Title must be 150 characters or less
\title[Tracer 1.6]{Bayesian MCMC diagnostics and summarisation using Tracer 1.6}

@@

\begin{figure}[ht]
\centerline{
\includegraphics[width=0.45\textwidth]{./figures/tracer.pdf}
}
\caption{The system design of Tracer 1.6}
\label{fig:tracer}
\end{figure}

@@

\begin{figure}[ht]
\includegraphics[width=.5\textwidth]{./figures/multitrace.png}
\caption{A comparison of multiple traces}
\label{fig:multitrace}
\end{figure}

@@

\begin{figure}[ht]
\subfigure[TangHuLu chart]{\includegraphics[width = .23\textwidth, height = 3cm]{./figures/tanghulu.pdf}}
\subfigure[boxplot]{\includegraphics[width = .23\textwidth, height = 3cm]{./figures/boxplot.pdf}}
\caption{Visualisation of joint-marginal distribution (a) between two integer or categorical traces using TangHuLu chart, and (b) between one continuous trace and one integer or categorical trace using box-and-whisker plot.}
\label{fig:tanghulu}
\end{figure}

@@

\begin{figure}[ht]
%\includegraphics[width=.5\textwidth]{./figures/fluBSP.pdf}
\subfigure[Bayesian coalescent skygrid]{\includegraphics[width = .23\textwidth]{./figures/fig21.png}}
\subfigure[Lineages through time]{\includegraphics[width = .23\textwidth]{./figures/fluLTT.pdf}}
\caption{(a) Bayesian coalescent skygrid plot and (b) lineages through time for the Influenza A/H3N2 virus data.}
\label{fig:flu}
\end{figure}

>>>>

% Title must be 150 characters or less
\title[Tracer 1.6]{Posterior summarisation in Bayesian phylogenetics using Tracer 1.6}

@@

% MAS: We need to limit the number of figures
%\begin{figure}[ht]
%\centerline{
%\includegraphics[width=0.45\textwidth]{./figures/tracer.pdf}
%}
%\caption{The system design of Tracer 1.6}
%\label{fig:tracer}
%\end{figure}

@@

\begin{figure}[ht]
%\includegraphics[width=.5\textwidth]{./figures/multitrace.png}
\subfigure[Multiple traces]{\includegraphics[width=0.46\textwidth]{./figures/multitrace.png}}
\subfigure[TangHuLu chart]{\includegraphics[width = .23\textwidth, height = 3cm]{./figures/tanghulu.pdf}}
\subfigure[boxplot]{\includegraphics[width = .23\textwidth, height = 3cm]{./figures/boxplot.pdf}}
\caption{A comparison of multiple traces}
\label{fig:multitrace}
\end{figure}

@@

%\begin{figure}[ht]
%\subfigure[TangHuLu chart]{\includegraphics[width = .23\textwidth, height = 3cm]{./figures/tanghulu.pdf}}
%\subfigure[boxplot]{\includegraphics[width = .23\textwidth, height = 3cm]{./figures/boxplot.pdf}}
%\caption{Visualisation of joint-marginal distribution (a) between two integer or categorical traces using TangHuLu chart, and (b) between one continuous trace and one integer or categorical trace using box-and-whisker plot.}
%\label{fig:tanghulu}
%\end{figure}

@@

\begin{figure}[ht]
%\includegraphics[width=.5\textwidth]{./figures/fluBSP.pdf}
%\subfigure[Bayesian coalescent skygrid]{\includegraphics[width = .23\textwidth]{./figures/fig21.png}}
\centerline{
\includegraphics[width=0.4\textwidth]{./figures/fig21.png}
}
% MAS: Please use vector-graphic format, like PDF
%\subfigure[Lineages through time]{\includegraphics[width = .23\textwidth]{./figures/fluLTT.pdf}}
\caption{(a) Bayesian coalescent skygrid plot and (b) lineages through time for the Influenza A/H3N2 virus data.}
\label{fig:flu}
\end{figure}
